Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-22 bbbq_article.tex
Fix supmat
Remove duplicate label
Updates from Overleaf

The earlier study defines a peptide a binder (for a haplotype), 
if \emp{within the peptide} in which it is found, 
is within the peptides with the 2\% lowest IC50 values.
This can be seen at \url{https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/master/predict-binders.R},
where the binders are written to file.

In this study, a peptide is defined a binder (for a haplotype), 
if within a \emp{proteome} in which it is found, 
is within the peptides with the 2\% lowest IC50 values,
where our previous study used the lowest 2\% IC50 values
within each \emp{protein}.
Subsection \ref{subsec:ic50s_per_haplotype} shows the IC50 values
for a binder per haplotype.

@@

Table \ref{tab:snp_stats} shows the statistics for all
SNPs, where tables \ref{tab:snp_stats_per_spanner_single}
and \ref{tab:snp_stats_per_spanner_multi} show the
statistics for only single-spanners and multi-spanners respectively.
These probabilities are also displayed visually in 
figures \ref{fig:ppoisbinom} (all proteins), \ref{fig:ppoisbinom_single} (single-spanners)
and \ref{fig:ppoisbinom_multi} (multi-spanners).

>>>>

The earlier study defines a peptide a binder (for a haplotype), 
if \emph{within the peptide} in which it is found, 
is within the peptides with the 2\% lowest IC50 values.
This can be seen at \url{https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/master/predict-binders.R},
where the binders are written to file.

In this study, a peptide is defined a binder (for a haplotype), 
if within a \emph{proteome} in which it is found, 
is within the peptides with the 2\% lowest IC50 values,
where our previous study used the lowest 2\% IC50 values
within each \emph{protein}.
Subsection \ref{subsec:ic50s_per_haplotype} shows the IC50 values
for a binder per haplotype.

@@

Table \ref{tab:snp_stats} shows the statistics for all
SNPs, where tables \ref{tab:snp_stats_per_spanner_single}
and \ref{tab:snp_stats_per_spanner_multi} show the
statistics for only single-spanners and multi-spanners respectively.
